Insert the article title here

### 2018-08-08 writeup/manuscript.tex
Working on intro

Anybody who has ever conducted a visual search experiment will be aware of the large differences from one participant to the next. These differences could be emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments, and search strategies\cite{boot2006}. Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.

In the current study, we focus on one source of individual differences in visual search: strategy. By visual search strategies, we refer to a collection of behaviours that all observers can freely choose to engage in when they search a display, which is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation. Perhaps surprisingly, previous literature has shown that both ideal oberver \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise. These apparent contradictory results could potentially expained by large individual differences. Search strategy can also vary in how systematic is it. For example it is common to see top-to-bottom and left-to-right scanning behaviour in scanpaths recorded during visual search\cite{gilchrist2006}, and the degree to which this occurs is in part related to the structure of the stimuli \cite{amor2017}.

>>>>

As is common in cognitive psychology, most visual search literature has focused on how the average participant performs in the task, despite it being well known that there is a great deal of variability between one subject and the next. These differences can emerge from several different sources of variation: tiredness\cite{mackworth1948}, information-processing ability, speed-accuracy trade-off, motivation, visual impairments \cite{nowakowska2016}, and search strategies\cite{boot2006}. Although their existence has previously been noted \cite{mackworth1948}, a rigorous examination of individual differences in visual search has been largely ignored and questions about their importance and stability remain relatively under explored.

In the current study, we focus on one source of individual differences in visual search: strategy. By search strategies, we refer to a collection of behaviours that all observers can freely choose from when they search a display. Examples include choosing to adopt a systematic left-to-right and top-to-bottom strategy, or the type of guided search behaviour in which locations that are more likely to contain the target are prioritised \cite{}.   This is distinct from intrinsically unchanging characteristics such as information-processing ability and motivation. Perhaps surprisingly, previous literature has shown that both ideal observer \cite{najemnik-geisler2008} and stochastic \cite{clarke2016} models can explain the number of fixations required by an average observer to locate a target in noise. These apparent contradictory results could potentially explained by large individual differences. Search strategy can also vary in how systematic is it. For example it is common to see top-to-bottom and left-to-right scanning behaviour in scan-paths recorded during visual search\cite{gilchrist2006}, and the degree to which this occurs is in part related to the structure of the stimuli \cite{amor2017}.
